---
title: "assignment02"
author: "Weijia Hu"
date: "2020/9/23"
output: html_document
---

```{r}
library(data.table)
library(leaflet)
library(tidyverse)
library(dplyr)

```
# Data Wrangling
### Merge the data
```{r}
indi <- data.table::fread("E:/566/aasignment2/chs_individual.txt")
regi <- data.table::fread("E:/566/aasignment2/chs_regional.txt")
dat <- merge(x=indi,y=regi,
           by.x="townname", by.y="townname",
           all.x=TRUE,all.y=FALSE)
```

```{r}
dat[,bmi_mh:=mean(bmi,na.rm=TRUE),by=.(male, hispanic)]
dat[,fev_mh:=mean(fev,na.rm=TRUE),by=.(male, hispanic)]

dat[,bmi:=ifelse(is.na(bmi),bmi_mh,bmi)]
dat[,fev:=ifelse(is.na(fev),fev_mh,fev)]
```
### 1. After merging the data, make sure you don’t have any duplicates by counting the number of rows. Make sure it matches.

```{r}
nrow(dat) == nrow(indi)
```

### 2.Create a new categorical variable named “obesity_level” using the BMI measurement (underweight BMI<14; normal BMI 14-22; overweight BMI 22-24; obese BMI>24). To make sure the variable is rightly coded, create a summary table that contains the minimum BMI, maximum BMI, and the total number of observations per category.

```{r}
dat[bmi<14, obesity_level := "underweight"]
dat[bmi>=14 & bmi<22, obesity_level := "normal"]
dat[bmi>=22 & bmi<24, obesity_level := "overweight"]
dat[bmi>=24, obesity_level := "obese"]

dat[,.(
  bmi_min = min(bmi, na.rm=T),
  bmi_max = max(bmi, na.rm=T),
  n= length(bmi)
),by =  obesity_level] [order( obesity_level)]
```
### 3.Create another categorical variable named “smoke_gas_exposure” that summarizes “Second Hand Smoke” and “Gas Stove.” The variable should have four categories in total.
```{r}
dat[smoke==0 & gasstove ==0, smoke_gas_exposure := "1"]
dat[smoke==1 & gasstove ==0, smoke_gas_exposure := "2"]
dat[smoke==0 & gasstove ==1, smoke_gas_exposure := "3"]
dat[smoke==1 & gasstove ==1, smoke_gas_exposure := "4"]
dat[,.(
   n= length(smoke)
), by = smoke_gas_exposure][order( smoke_gas_exposure)]
```
### 4. Create four summary tables showing the average (or proportion, if binary) and sd of “Forced expiratory volume in 1 second (ml)” and asthma indicator by town, sex, obesity level, and “smoke_gas_exposure.”

```{r}
#Townname
dat[,.(
   fev_mean = mean(fev, na.rm=T),
   fev_sd = sd(fev, na.rm=T)
), by = townname][order(townname)]
```

```{r}
#Sex
dat[,.(
   fev_mean = mean(fev, na.rm=T),
   fev_sd = sd(fev, na.rm=T)
), by = male][order(male)]
```

```{r}
#Obesity level
dat[,.(
   fev_mean = mean(fev, na.rm=T),
   fev_sd = sd(fev, na.rm=T)
), by = obesity_level][order(obesity_level)]

```

```{r}
#smoke_gas_exposure
dat[,.(
   fev_mean = mean(fev, na.rm=T),
   fev_sd = sd(fev, na.rm=T)
), by = smoke_gas_exposure][order(smoke_gas_exposure)]

```

# Looking at the Data (EDA)
### 1. Facet plot showing scatterplots with regression lines of BMI vs FEV by “townname”.
```{r}
dat %>%
  filter(!(townname %in% NA)) %>%
  ggplot(mapping = aes(x= bmi, y=fev, color=townname))+
  geom_point(mapping=aes(color=townname))+
  stat_smooth(method = lm)+
  facet_wrap(~townname, nrow=2)
```

### 2.Stacked histograms of FEV by BMI category and FEV by smoke/gas exposure. Use different color schemes than the ggplot default.
```{r}
#The histogram of FEV by BMI category
dat %>%
  filter(!(obesity_level %in% NA)) %>%
  ggplot()+
  geom_histogram(mapping = aes(x = fev, fill=obesity_level))+
  scale_fill_brewer(palette = "Pastel1")+
  theme_bw()
```
```{r}
#The histogram of FEV by smoke/gas exposure
dat %>%
  filter(!(smoke_gas_exposure %in% NA)) %>%
  ggplot()+
  geom_histogram(mapping = aes(x = fev, fill=smoke_gas_exposure))+
  scale_fill_brewer(palette = "Pastel1")+
  theme_bw()
```
### 3. Barchart of BMI by smoke/gas exposure.
```{r}
dat %>%
  filter(!(smoke_gas_exposure %in% NA)) %>%
  ggplot()+
  geom_bar(mapping = aes(x= obesity_level, fill=smoke_gas_exposure))+
  scale_fill_brewer(palette = "Pastel1")
```

### 4. Statistical summary graphs of FEV by BMI and FEV by smoke/gas exposure category.
```{r}
dat %>%
  ggplot(mapping=aes(x=obesity_level, y=fev))+
  stat_summary(fun.data="mean_sdl")

dat %>%
  filter(!(smoke_gas_exposure %in% NA)) %>%
  ggplot(mapping=aes(x=smoke_gas_exposure, y=fev))+
  stat_summary(fun.data="mean_sdl")
```

### 5. A leaflet map showing the concentrations of PM2.5 mass in each of the CHS communities.
```{r}
dat2<-dat[!is.na(pm25_mass)]
pm25_pal = colorNumeric(c('darkgreen','goldenrod','brown'), domain=dat2$pm25_mass)
leaflet(dat2)%>%
  addProviderTiles("OpenStreetMap")%>%
  addCircles(lat=~lat,lng=~lon,color=~pm25_pal(pm25_mass),opacity=1,fillOpacity=1, radius=5000)%>%
addLegend("bottomleft", pal=pm25_pal,values =dat2$pm25_mass, title="concentration of PM2.5 Mass", opacity=1)
```

### 6. Choose a visualization to examine whether PM2.5 mass is associated with FEV.

```{r}
dat %>%
  filter(!(pm25_mass %in% NA)) %>%
  ggplot(mapping = aes(x= pm25_mass, y=fev))+
  geom_point()+
  stat_smooth(method = lm)

```

### The primary questions of interest are: 
1. What is the association between BMI and FEV (forced expiratory volume)? 

-Based on the question 1, there is a positive association between BMI and FEV among these towns. 

2. What is the association between smoke and gas exposure and FEV? 

-I think there is an association between smoke and gas exposure and FEV. But the distributions of FEV are normal among every smoke and gas group. 

3. What is the association between PM2.5 exposure and FEV?

-According to the last question, the regression line is almost horizontal. We could say that there is a weak negative association between PM2.5 exposure and FEV. But I'd rather conclude that there is no association between PM2.5 exposure and FEV.
