---
title: "assignment03"
author: "Weijia Hu"
date: "2020/10/14"
output: html_document
---

```{r}
library(httr)
library(xml2)
library(stringr)
library(knitr)
```

# APIs

- Using the NCBI API, look for papers that show up under the term "sars-cov-2 trial vaccine." Look for the data in the pubmed database, and then retrieve the details of the paper as shown in lab 7. How many papers were you able to find?

```{r counter-pubmed, eval=TRUE, cache=TRUE}
# Downloading the website
website <- xml2::read_html("https://pubmed.ncbi.nlm.nih.gov/?term=sars-cov-2+trial+vaccine")
# Finding the counts
counts <- xml2::xml_find_first(website, "/html/body/main/div[9]/div[2]/div[2]/div[1]/span")
# Turning it into text
counts <- as.character(counts)
# Extracting the data using regex
stringr::str_extract(counts, "[0-9,]+")
```

- There are 563 paper that I'm able to find. 

- Using the list of pubmed ids you retrieved, download each papers’ details using the query parameter rettype = abstract. If you get more than 250 ids, just keep the first 250.

```{r, eval=TRUE}

query_ids <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/esearch.fcgi",
  query = list(
    db ="pubmed",
    term= "sars-cov-2 trial vaccine",
    retmax=  250
  )
)
# Extracting the content of the response of GET
ids <- httr::content(query_ids)
```

- As we did in lab 7. Create a dataset. 
### Pubmed ID number
```{r get-ids, eval = TRUE}
# Turn the result into a character vector
ids <- as.character(ids)
# Find all the ids 
ids <- stringr::str_extract_all(ids, "<Id>[0-9]+</Id>")[[1]]
# Remove all the leading and trailing <Id> </Id>. Make use of "|"
ids <- stringr::str_remove_all(ids, "<Id>|</Id>")
```

```{r get-abstracts, eval = TRUE}
publications <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/efetch.fcgi",
  query = list(
    db= "pubmed",
    id = paste(ids, collapse = ","),
    retmax = 250,
    rettype = "abstract"
    )
)
# Turning the output into character vector
publications <- httr::content(publications)
publications_txt <- as.character(publications)
```

```{r one-string-per-response, eval = TRUE}
pub_char_list <- xml2::xml_children(publications)
pub_char_list <- sapply(pub_char_list, as.character)
```
### Abstract of the paper 
```{r extracting-last-bit, eval = TRUE}
abstracts <- str_extract(pub_char_list, "<Abstract>(\\n|.)+</Abstract>")
abstracts <- str_remove_all(abstracts, "</?[[:alnum:]]+>")
abstracts <- str_replace_all(abstracts, "\\s+", " ")
```
### Title of the paper
```{r process-titles, eval = TRUE}
titles <- str_extract(pub_char_list, "<ArticleTitle>(\\n|.)+</ArticleTitle>")
titles <- str_remove_all(titles, "</?[[:alnum:]]+>")
titles <- str_replace_all(titles, "\\s+", " ")
```
### Name of the journal where it was published
```{r}
journals <- str_extract(pub_char_list, "<Title>(\\n|.)+</Title>")
journals <- str_remove_all(journals, "</?[[:alnum:]]+>")
journals <- str_replace_all(journals, "\\s+", " ")
```
### Publication date
```{r}
dates <- str_extract_all(pub_char_list, "<PubDate>(\\n|.)+</PubDate>")
dates <- str_remove_all(dates, "</?[[:alnum:]]+>")
dates <- str_replace_all(dates, "\\s+", " ")
```


```{r build-db, eval = TRUE}
database <- data.frame(
  PubMedID = ids,
  Title = titles,
  Journal=journals,
  PublicationDate=dates,
  Abstract = abstracts
)
knitr::kable(database)
```
# Text Mining

```{r}
library(readr)
library(dplyr)
library(tidytext)
library(ggplot2)
```

```{r}
txt_m <- read_csv("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/03_pubmed/pubmed.csv")
```

## 1.Tokenize the abstracts and count the number of each token. Do you see anything interesting? Does removing stop words change what tokens appear as the most frequent? What are the 5 most common tokens for each search term after removing stopwords?
```{r}
library(forcats)
txt_m %>%
  unnest_tokens(output =  token, input = abstract) %>%
  count(token, sort=T)%>%
  top_n(n=20, wt=n)%>%
  ggplot(aes(x=n, y=fct_reorder(token,n)))+
  geom_col()
```

- The top 7 words are stop words. So, let's remove the stop words.

```{r}
txt_m %>%
  unnest_tokens(word, abstract)%>%
  anti_join(tidytext::stop_words)%>%
  count(word, sort=T)%>%
  top_n(20,n)%>%
  ggplot(aes(x=n, y=fct_reorder(word, n)))+
  geom_col()
```

- After removing stop words, we could find that the top 1 word is "covid", followed by "patients" and "cancer".


```{r}
txt_m %>%
  unnest_tokens(word, abstract)%>%
  anti_join(tidytext::stop_words)%>%
  group_by(term)%>%
  count(word)%>%
  top_n(5,n)
```

- The 5 most common tokens for each search term after removing stop words are shown. 

## 2. Tokenize the abstracts into bigrams. Find the 10 most common bigram and visualize them with ggplot2.
```{r}
txt_m %>%
 unnest_ngrams(word, abstract, n = 2) %>%
 count(word, sort = TRUE)%>%
 top_n(10,n)%>%
 ggplot(aes(x=n, y=fct_reorder(word, n)))+
 geom_col()
```
- I noticed that the second and third words are all stop words. So, let's remove the stop words again.

```{r}
library(tidyr)
txt_m2 <- txt_m %>%
  unnest_ngrams(output=word, input=abstract ,n=2)%>%
  separate (col = word, into = c("word1", "word2"),sep = " ")%>%
  anti_join(
    tidytext::stop_words, by =c("word1" = "word")
  ) %>%
  anti_join(
    tidytext::stop_words, by =c("word2" = "word")
  ) %>%

  unite(txt_m21, word1, word2, sep= " ")

txt_m2 %>%
  count(txt_m21, sort = TRUE)%>%
 top_n(10,n)%>%
 ggplot(aes(x=n, y=fct_reorder(txt_m21, n)))+
 geom_col()
```

- After removing the stop words, The "covid 19" is the top 1 bigram. 

## 3. Calculate the TF-IDF value for each word-search term combination. (here you want the search term to be the “document”) What are the 5 tokens from each search term with the highest TF-IDF value? How are the results different from the answers you got in question 1?

```{r}
txt_m1 <- txt_m %>%
  unnest_tokens(abstract, abstract) %>% 
  filter(!(abstract %in% stop_words$word)) %>%
  count(abstract, term) %>%
  group_by(term)%>%
  bind_tf_idf(abstract, term, n) %>%
  top_n(5, n) %>%
  arrange(desc(tf_idf))

txt_m1 %>%
    group_by(term)%>%
arrange(desc(tf_idf))
```

- The top 5 tokens for term "Covid": covid, pandemic, 19, disease and patients.
- The top 5 tokens for term "prostate cancer": prostate, cancer, disease, patients and treatment.
- The top 5 tokens for term "preeclampsia": eclampsia, preeclampsia, pregnancy, pre and treatment.
- The top 5 tokens for term "meningitis": meningitis, meningeal, csf, clinical and patients.
- The top 5 tokens for term "cystic fibrosis": cf, fibrosis, cystic, disease and patients. 

The results in this question are not similar to them in the first question. I think results in this question are more meaningful. More important information comes more first. 